### 2022-05-02 paper/ase22/experiment.tex
exp

\begin{enumerate}[label=\textbf{RQ\arabic*}]
\item \label{rq:one}: Can \tool generate test cases with the correct \lc categorization and
  sentiment label?
\item \label{rq:two}: Can \tool generate more diverse test cases than \Cklst?
\item \label{rq:three}: Can \tool be useful to find root causes of bugs in the \sa models?
%% \item \label{rq:three}: How effective is our new test case generation
%%   using \cfg expansion? % ablation study
\end{enumerate}

@@

\sw{@Jaeseong: rewrite the next two paragraphs to reflect the updated manual study. Also, be explicit about the setup: sample size, population size, number of participants, protocol (each given how many sentences, and how disagreement is resolved), etc.}
In the manual study, we sample a set of test cases and corresponding \lc randomly sampled
from seed sentences and expanded sentences from \tool. 
also provided with the sampled test cases. Each subject is asked for
scoring relevancy between the linguistic capability of the
sentences. The score is discrete and it ranges from 1 to 5
representing ``strongly not relevant'' to ``strongly relevant''
respectively. Additionally, the subject scores the relevancy between
sentences and their sentiment labels. The score is also discreate and
ranges from 1 to 5. It represents ``strongly negative'' to ``strongly
positive'' respectively. In this work, we collect manual study scores
from 8 subjects attended. From the collected scores, we measure the
following metrics:

>>>>

\begin{enumerate}[label=\textbf{RQ\arabic*}]
\item \label{rq:one}: Can \tool generate consistent test sentence and
  its oracle?
\item \label{rq:two}: Is \tool generated testcases relevant to be used
  for their \lc evaluation?
\item \label{rq:three}: Can \tool generate more diverse test cases
  than \Cklst?
\item \label{rq:four}: Can \tool be useful to find root causes of bugs
  in the \sa models?
%% \item \label{rq:three}: How effective is our new test case generation
%%   using \cfg expansion? % ablation study
\end{enumerate}

@@

\sw{@Jaeseong: rewrite the next two paragraphs to reflect the updated
  manual study. Also, be explicit about the setup: sample size,
  population size, number of participants, protocol (each given how
  many sentences, and how disagreement is resolved), etc.}

In the manual study, we sample a set of test cases and corresponding
\lc randomly sampled from seed sentences and expanded sentences from
\tool.  also provided with the sampled test cases. Each subject is
asked for scoring relevancy between the linguistic capability of the
sentences. The score is discrete and it ranges from 1 to 5
representing ``strongly not relevant'' to ``strongly relevant''
respectively. Additionally, the subject scores the relevancy between
sentences and their sentiment labels. The score is also discreate and
ranges from 1 to 5. It represents ``strongly negative'' to ``strongly
positive'' respectively. In this work, we collect manual study scores
from 8 subjects attended. From the collected scores, we measure the
following metrics:
